\chapter{Dan Cristofaro-Gardiner: Low-Action Holomorphic Curves and Invariant Sets}
\label{cristofaro}

\abstract{I will discuss a new compactness theorem for sequences of low-action punctured holomorphic curves of controlled topology, in any dimension, without imposing the typical assumption of uniformly bounded Hofer energy; in the limit, we extract a family of closed Reeb-invariant subsets. I will also explain why such sequences exist in abundance in low-dimensional symplectic dynamics, via the theory of embedded contact homology. This has various applications: the one I want to focus on in my talk is a generalization to higher genus surfaces and three-manifolds of the celebrated Le Calvez–Yoccoz theorem. All of this is joint with Rohil Prasad.}

\section{Introduction}

\subsection{A New Compactness Theorem }

Consider a closed oriented $2n+1$ manifold $Y$. We are interested in framed Hamiltonian structures:

\begin{definition}

A \textbf{framed Hamiltonian structure} is a pair $(\lambda,\omega)$ where $\lambda$ is a 1-form, $\omega$ is a closed 2-form, and $\lambda \wedge \omega^n > 0$.

\end{definition}

\begin{example}
\text{ }
\begin{itemize}
\item Let $\lambda$ be a contact form, $\omega =\,d\lambda$. The mapping torus is a symplectic automorphism $\phi: (M^{2n}, \omega) \to (M^{2n}, \omega)$. We have
    \[
    Y=M^{2n}\times [0,1]/\sim
    \]
    where $(x,1) \sim (\phi(x), 0)$. The pair $(dt, \omega)$ is a framed Hamiltonian structure.
\item Suppose we have a proper Hamiltonian $H:(M^{2n}, \omega) \to R$. Suppose we have a regular value $c$. Then $H^{-1}(c)$ is a framed Hamiltonian structure.
\item Non-singular volume preserving flows on a closed 3-manifold are framed Hamiltonian structures.
\end{itemize}

\end{example}

Let $(\lambda, \omega)$ is a Hamiltonian vector field. Suppose we have $R$ satisfying $\omega(R, \cdot)=0, \lambda(R)=1$.

\begin{example}

In the contact case, $R$ is the Reeb vector field.

\end{example}

We want non-trivial (nonempty and proper) closed invariant sets of $R$.

\begin{example}
\text{ }
\begin{itemize}
\item A periodic orbit
\item The invariant tori
\item Orbit closure for $f$ proper
\end{itemize}

\end{example}

Consider the symplectization $X=\mathbb{R}\times Y$ with an almost complex structure: $J: TX\to TX, J^2=-1, J(\partial_S)=R$ that preserves $\text{ker}(\lambda)$ compatibly with $\omega$. We are interested in sequences of holomorphic curves
\[
u_k: C_k \to \mathbb{R}\times Y
\]
where $u_k$ is proper and $J$-holomorphic, $C_k$ is a closed Riemann surface minus a finite number of punctures. For $u_k$, define the limit set
\[
L(u_k) = \{ \overline{K}\subset (-1, 1)\times Y | \text{condition}\}
\]
where the condition is that $\overline{k}$ is closed and there exists a subsequence $u_k(C_k) \cap (s_k-1, s_k+1)\times Y$ converging (after shifting) to $k$. We should think of this as subsequential limits of height 2 slices.

\begin{proposition}

$L(u_*)$ is a connected.

\end{proposition}

We have the following classical quantities associated to $u$:
\begin{itemize}
\item The action
    \[
    \mathcal{A}(u) = \int_C u^* \omega
    \]
\item The Hofer energy
    \[
    \mathcal{E}(u)=\sup_{s\in \mathbb{R}} \int_{C\cap u^{-1}(\{s\}\times Y)} u^*\lambda
    \]
\end{itemize}

\begin{theorem}

Let $u_k: C_k \to R\times Y$ be such that $\lim_{k\to \infty} \mathcal{A}(u_k)=0$ and $\inf_k x(C_k)>-\infty$. Then every $k\in L(u_*)$ satisfies $k=(-1,1) \times \Lambda$ for some closed non-empty invariant set $\Lambda$.

\end{theorem}

The upshot is that the sequence as in the theorem gives a connected family of invariant sets.

\begin{remark}

The main novelty is that there is no bound required on the Hofer energy $\mathcal{E}(u_k)$.

\end{remark}

\section{Dynamical Applications}

The upshot is that the theorem widely applicable in low dimensions. In higher dimensions, problems are more open. In particular, they are very important in relation to the Le Calvez-Yoccoz Theorems

\begin{definition}
[Birkhoff]

A dynamical system $Y$ is \textbf{minimal} if every orbit is dense.

\end{definition}

One motivation is that if $Y$ is not minimal, we can write $Y=k \cap (Y-k)$ where $k$ is a non-trivial invariant set.

\begin{problem}
[Ulam]

Is there a minimal homeomorphism of $\mathbb{R}^n$ or $\mathbb{R}^n - \{p\}$?

\end{problem}

\begin{theorem}
[Le Calvez, Yocroz, 1997]

A homeomorphism of $S^2-\{p_1,...,p_k\}$ is never minimal.

\end{theorem}

\begin{definition}

A system has the \textbf{(strong) Le Calvez-Yoccoz property} if the complement of any nontrivial invariant set is never minimal.

\end{definition}

\begin{theorem}
[Cristofaro-Gardiner, Prasad]

The following have the strong Le Calvez-Yoccoz property:

\begin{enumerate}
\item Any Hamiltonian diffeomorphism of a closed surface
\item Any Reeb flow on a rational homology sphere
\item Any geodesic flow on a closed surface (considered as a flow of its unit tangent bundle)
\end{enumerate}

\end{theorem}

\begin{remark}

There is no genericity required.

\end{remark}

\begin{corollary}

$(1)-(3)$ have the property that the non-trivial invariant sets are dense

\end{corollary}

\begin{corollary}

Any geodesic flow on a surface has the property that a dense set of points have $n$ non-dense geodesic passing through them.

\end{corollary}

\section{Proof Ideas}

\subsection{Finding Low Action Curves of Controlled Topology}

This part of the proof uses the embedded contact homology $\text{ECH}$. For $(Y, \lambda)$ a closed 3-manifold, $\text{ECH}(Y,\lambda)$ is a homology of a cochain complex that counts (mostly) embedded curves.

\begin{theorem}

\[
\text{ECH}(X, \lambda) \cong \text{HM}(Y)
\]

\end{theorem}

There exists a map $u: \text{ECH}\to \text{ECH}$ bounding curves through a marked point and the Weyl law allows us to use the $u$-map to produce low action curves

\begin{problem}

How do we bound $X_\pi(C_k)?$

\end{problem}

There is no bound a priori on the genus.

\begin{theorem}
[Cristofaro, Gardiner, Prasad]

\[
x_k(C_k)\ge -2.
\]

\end{theorem}

\subsection{Proving the Compactness Theorem}

The main point is a new estimate that bounds of $C$ in a small ball if $C$ is low action in terms of $\chi(C)$.