\chapter{Thomas Massoni: Taut Foliations Through a Contact Lens}
\label{massoni}
    
\abstract{In the late ’90s, Eliashberg and Thurston established a remarkable connection between foliations and contact structures in dimension three: any co-oriented, aspherical foliation on a closed, oriented 3-manifold can be approximated by both positive and negative contact structures. Additionally, if the foliation is taut then its contact approximations are tight. In this talk, I will present a converse result on constructing taut foliations from suitable pairs of contact structures. While taut foliations are rather rigid objects, this viewpoint reveals some degree of flexibility and offers a new perspective on the $L$-space conjecture.}

\section{Introduction}

Let $M^2$ be a closed, oriented, connected 3-manifold.

Informally, a foliation $\mathcal{F}$ is made by decomposing $M$ into 2d leaves. If such a foliation is smooth, we can define $T\mathcal{F}=\text{Ker }\alpha$, where $\alpha$ is a 1-form.

\begin{theorem}
[Frobenius Integrability Theorme]
\[
\alpha \wedge \,d\alpha=0.
\]
\end{theorem}

\begin{definition}

The \textbf{minimally integrable plane field} is
\[
\xi = \text{Ker }(\alpha)
\]
where $\alpha$ is a 1-form satisfying
\[
\alpha \wedge d\alpha \neq 0
\]

\end{definition}

Locally, we have the following theorem:

\begin{theorem}
[Darboux]
\[
\alpha = \,dz+x\,dy
\]
\end{theorem}

\begin{theorem}

Every homotopy class of a plane field is defined up to foliation.

\end{theorem}

\begin{proof}
Follows from the $h$-principal.
\end{proof}

\begin{theorem}
[Eliashberg]

The same holds for contact structures.

\end{theorem}


\begin{definition}

A \textbf{taut foliation} satisfies the following properties:
\begin{itemize}
\item for all $p\in M$, there exists $\gamma$ cloosed loop passing through $p$, where $\gamma$ transverses $\mathcal{F}$.
\item there exists $\omega$ a closed 2-form satisfying $\omega_{T\mathcal{F}}>0$.
\end{itemize}

\end{definition}

We present the following (badly defined) definition.

\begin{definition}

A \textbf{tight contact structures} is a structure that isn't over-twisted.

\end{definition}

\begin{problem}

Which $M$ carry a taut foliation? Reebless foliation? Tight contact structure?

\end{problem}

\begin{theorem}

If the first Betti number $b_1(H)>0$, there exists a taut foliation.

\end{theorem}

\begin{theorem}
[Eliashberg, Thurson]

There exists tight contact structures.

\end{theorem}

\begin{problem}

What happens for $b=1$, equivalently $QHS^3$?

\end{problem}

\begin{conjecture}
[L-Space Conjecture]

Let $M$ be $QHS^3$, irreducble, The following are equivalent:
\begin{enumerate}
\item $M$ causes a taut foliation
\item $M$ is not an $L$-space: $\text{HF}^{\text{red}}=0$
\item $\pi_1(M)$ is left-orderable
\end{enumerate}

\end{conjecture}

We have the following progress so far:

\begin{theorem}
[Ozsvath, Szabo]
\[
(1)\implies (2)
\]
\end{theorem}

But in general, it's unsolved and people think it's wrong.

The punchline is taut foliations can be thought of as contact geometry objects.

\section{From Foliations to Contact Structures}

\begin{theorem}
[Eliashberg, Thurston, 1998]

\begin{enumerate}
\item For a $\mathcal{F}$ foliation $(C^2)$ with no spherical leaf (meaning no $\mathcal{F}=S^2 \times \{\text{pt}\}$ on $S^1\times S^2$), then $T\mathcal{F}$ $t_L$ are approximately contact structures.
\item If $\mathcal{F}$ taut, then the contact structures are tight.
\end{enumerate}

\end{theorem}

\subsection{Proof of $(2)$}

\begin{proof}
Look at $[-1, 1]\times M$, choose $\omega$ closed in $M$, $w|_{T\mathcal{F}}>0$, and choose $\alpha$ a 1-form such that $T\mathcal{F}=\ker \alpha$.

Suppose $\Omega = \omega(t\alpha)$. If $\xi_{\pm}$ weak symplectic filling of $(-M, \xi_-) \sqcup (M, \xi_+)$. If $\xi_\pm$ $C^0$-close to $T\mathcal{F}$, then $\Omega$ is symplectic and $\Omega|_{\xi_\pm}>0$.

By [Gromov, Eilenberg], $\xi_+$ is tight.
\end{proof}

\begin{definition}

A $C^0$-foliation is a topological foliation where the leaves are smoothly immersed and $T\mathcal{F}$ is $C^0$

\end{definition}

\begin{theorem}
[Bowden, Kasez, Robert]

Eliashberg-Thurson holds for $C^0$-foliations.

\end{theorem}

We should think of Eliashberg-Thurson as a machine that turns a foliation into a postiive contact pair $(\xi_-, \xi_+)$.

\section{From Positive Constant Pairs to Foliations}

\begin{definition}

We say $(\xi_-, \xi_+)$ is a \textbf{positive contact pair} if $\xi_\pm$ is a $\pm$ contact structure and there exists a vector field $Z$ such that $Z$ positively transverses $\xi_\pm$.

\end{definition}

Fix $(\xi_+, \xi_-)$ and $Z$.

\begin{theorem}
[Massoni, 2024]

Assume that at least one of $\xi_\pm$ is right, or $\xi_-$ and $\xi_+$ are transverse. Then there exists a foliation $\mathcal{F}$ that transverses to $Z$.

\end{theorem}

\begin{definition}

If there exists a $Z$ which is volume preserving, then we say $(\xi_-, \xi_+)$ is \textbf{strongly right}.

\end{definition}

A corollary of the theorem is as follows:

\begin{corollary}

$M\neq S^1\times S^2$ admits a taut foliation if and only if it admits a strongly tight contact pair.

\end{corollary}

\subsection{Sketch of Proof Idea }

Consider a vector field $X\subset \xi_- \cap \xi_+$ which vanishes exactly along
\[
\Delta = \{ p\in M| \xi_-(p) = \xi_+(p)\}
\]

Consider $\xi_\pm^t= (\phi_x^t) \times \xi_\pm$.

\begin{proposition}

There exists $\eta$ a continuous plane field such that $\xi_\pm^t$ converges to $\eta$.

\end{proposition}

\begin{proposition}

The map $(\xi_-, \xi_+)\mapsto \eta$ is continuous.

\end{proposition}

\begin{proposition}

For generic $(\xi_-,\xi_+)$, $\eta$ is locally integrable.

\end{proposition}

Warning: $\eta$ is only $C^0$, not always uniquely integrable tangent to the foliation.

There is also the useful notion of branching foliation, which we will not define right now.

\begin{proposition}

Assume that there is no immersed $\overline{D}\to M$ tangent to $\eta$ such that $\partial \overline{D}^2$ tangent to $X$. Then $\eta$ is tangent to a branching foliation.

\end{proposition}

\begin{proposition}

$\eta$ is approximatable by integrable plane fields.

\end{proposition}

\section{Speculation}

Here is some speculation about the future of this area. Strongly tight pairs are hard to work with, but there are a few intruiging conjectures and problems to work on.

\begin{conjecture}
[Massoni]

If $(\xi_-, \xi_+)$ is a positive pair and both $\xi_\pm$ are tight, then there exists a Reebless foliation.

\end{conjecture}

We want an intrinsic result on the isotopy classes of $\xi_-$ and $\xi_+$.

\begin{problem}

Consider a contact pair $(\xi_-, \xi_+)$, not necessarily positive. Assume they are both tight, they are homotopic as plane fields, and $\langle c(\xi_-), c(\xi_+) \rangle=1$. Then does there exist a Reeb-less foliation on $M$?

\end{problem}

The third condition that we assumed is motivated by the following theorem:

\begin{theorem}
[Lin]

If $\mathcal{F}$ is a taut foliation, $\xi_\pm$ are contact approximations,
\[
\langle c(\xi_-), c(\xi_+) \rangle=1
\]
where $c$ is the contact invariant in $\text{HF}$.

\end{theorem}

Here is an application of this theorem:

\begin{theorem}

Take $M^2 \neq S^1 \times S^2$, with $\mathcal{F}$ a taut foliation on $M$ and $K$ a transverse and framed knot. Then there exists $s_0$ such that for every $s\in \mathbb{Q}$ with $|s|\ge s_0$, there exists a a taut foliation on $M_k(s)$ transverse to $K'$ (image of $K$).

\end{theorem}